The imputation methods big test

### 2020-04-27 pd2.Rmd
Prawie gotowy wykres (co z legendą?)

```{r imputation_basic_functions}
imputation_mode_median <- function(df){

@@

```{r imputation_advanced_functions, message = FALSE, warning = FALSE}
library(mice)
imputation_fun_mice <- function(df){
  init <- mice(df, maxit=0) 
  meth <- init$method
  predM <- init$predictorMatrix
  imputed <- mice(df, method=meth, predictorMatrix=predM, m=5)
  completed <- complete(imputed)
  return(completed)
}
library(VIM)
imputation_fun_vim <- function(df){
  no_columns <- length(df)
  imputed <- kNN(df)
  imputed <- imputed[,1:no_columns]
  return(imputed)
}
library(missForest)
imputation_fun_missForest <- function(df){
  return(missForest(df)$ximp)
}
```

@@

```{r read_dataset}
DFT_REPO_DATASET_DIR = './dependencies/datasets'
read_dataset <- function(openml_id, dataset_dir = DFT_REPO_DATASET_DIR){

@@

```{r read_all_datasets}
read_all_datasets <- function(dataset_dir = DFT_REPO_DATASET_DIR){

@@

```{r train_test_split}
set.seed(1357)
train_test_split <- function(dataset, train_size){
  smp_size <- floor(train_size * nrow(dataset))
  typeof(smp_size)

@@

```{r metrics}
get_confusion_matrix <- function(test, pred){
  return (table(Truth = test, Prediction = pred))
}
confusion_matrix_values <- function(confusion_matrix){
  TP <- confusion_matrix[2,2]
  TN <- confusion_matrix[1,1]
  FP <- confusion_matrix[1,2]
  FN <- confusion_matrix[2,1]
  return (c(TP, TN, FP, FN))
}
accuracy <- function(confusion_matrix){
  conf_matrix <- confusion_matrix_values(confusion_matrix)
  return((conf_matrix[1] + conf_matrix[2]) / (conf_matrix[1] + conf_matrix[2] + conf_matrix[3] + conf_matrix[4]))
}
precision <- function(confusion_matrix){
  conf_matrix <- confusion_matrix_values(confusion_matrix)
  return(conf_matrix[1]/ (conf_matrix[1] + conf_matrix[3]))
}
recall <- function(confusion_matrix){
  conf_matrix <- confusion_matrix_values(confusion_matrix)
  return(conf_matrix[1] / (conf_matrix[1] + conf_matrix[4]))
}
f1 <- function(confusion_matrix){
  conf_matrix <- confusion_matrix_values(confusion_matrix)
  rec <- recall(confusion_matrix)
  prec <- precision(confusion_matrix)
  return(2 * (rec * prec) / (rec + prec))
}
```

@@

```{r get_result_function, warning = FALSE, message = FALSE}
library(rpart)
get_result <- function(dataset_list, imputation_fun){

@@

```{r warning=FALSE}
  library(knitr)
  results <- c(list(0),list(0),list(0),list(0),list(0))
  results[[1]] <- readRDS('./part_results/res1_new.rds')
  results[[2]] <- readRDS('./part_results/res2_new.rds')
  results[[3]] <- readRDS('./part_results/res3_new.rds')
  results[[4]] <- readRDS('./part_results/res4_new.rds')
  results[[5]] <- readRDS('./part_results/res5_new.rds')

  result_table <- function(ds_it){
    d <- data.frame(matrix(ncol = 7, nrow = 0))
    colnames(d) <- c("imputation", "accuracy", "precision", "recall", "f1", "imp_time", "mod_time")
    for (i in 1:length(imputations)){
      if (length(results[[i]][[ds_it]]) != 1){ # length equal 1 means "ERROR" was generated in partial results 
        d[i,] <- c(results[[i]][[ds_it]]$imp_method,
               round(as.numeric(results[[i]][[ds_it]]$classification_report$accuracy),3),   
               round(as.numeric(results[[i]][[ds_it]]$classification_report$precision),3),
               round(as.numeric(results[[i]][[ds_it]]$classification_report$recall),3),
               round(as.numeric(results[[i]][[ds_it]]$classification_report$f1),3),
               round(as.numeric(results[[i]][[ds_it]]$imputation_time),3),
               # @TODO konwersja jednostek, as.numeric nie rozroznia jednostek czasu
               round(as.numeric(results[[i]][[ds_it]]$modelling_time),3)) 
      }
      else{ # for error input imputation name
        if (i==3){
          d[i,1] <- "imputation_fun_mice" 
        }
        if (i==4){
          d[i,1] <- "imputation_fun_missForest" 
        }
        if (i==5){
          d[i,1] <- "imputation_fun_vim" 
        }
      }
    }
    d
  }

  results[[1]]
  # change i bound to number of datasets 
  for (i in 1:length(results[[1]])){ # TUTAJ BANGLA DOPÓKI NIE WEŹMIE SIĘ KTÓREGOŚ ZE ZBIORÓW 4, 10, 11, 12, 13, 14 (czyli "nowych")
    kable(result_table(i), caption = paste("Dataset id: ", results[[2]][[i]]$dataset_id, sep = ""))
  }

@@

>>>>

```{r imputation_basic_functions, cache = TRUE}
imputation_mode_median <- function(df){

@@

```{r imputation_advanced_functions, message = FALSE, warning = FALSE, cache = TRUE}
library(mice)
imputation_fun_mice <- function(df){
  init <- mice(df, maxit=0) 
  meth <- init$method
  predM <- init$predictorMatrix
  imputed <- mice(df, method=meth, predictorMatrix=predM, m=5)
  completed <- complete(imputed)
  return(completed)
}
library(VIM)
imputation_fun_vim <- function(df){
  no_columns <- length(df)
  imputed <- kNN(df)
  imputed <- imputed[,1:no_columns]
  return(imputed)
}
library(missForest)
imputation_fun_missForest <- function(df){
  return(missForest(df)$ximp)
}
```

@@

```{r read_dataset, cache = TRUE}
DFT_REPO_DATASET_DIR = './dependencies/datasets'
read_dataset <- function(openml_id, dataset_dir = DFT_REPO_DATASET_DIR){

@@

```{r read_all_datasets, cache = TRUE}
read_all_datasets <- function(dataset_dir = DFT_REPO_DATASET_DIR){

@@

```{r train_test_split, cache = TRUE}
set.seed(1357)
train_test_split <- function(dataset, train_size){
  smp_size <- floor(train_size * nrow(dataset))
  typeof(smp_size)

@@

```{r metrics, cache = TRUE}
get_confusion_matrix <- function(test, pred){
  return (table(Truth = test, Prediction = pred))
}
confusion_matrix_values <- function(confusion_matrix){
  TP <- confusion_matrix[2,2]
  TN <- confusion_matrix[1,1]
  FP <- confusion_matrix[1,2]
  FN <- confusion_matrix[2,1]
  return (c(TP, TN, FP, FN))
}
accuracy <- function(confusion_matrix){
  conf_matrix <- confusion_matrix_values(confusion_matrix)
  return((conf_matrix[1] + conf_matrix[2]) / (conf_matrix[1] + conf_matrix[2] + conf_matrix[3] + conf_matrix[4]))
}
precision <- function(confusion_matrix){
  conf_matrix <- confusion_matrix_values(confusion_matrix)
  return(conf_matrix[1]/ (conf_matrix[1] + conf_matrix[3]))
}
recall <- function(confusion_matrix){
  conf_matrix <- confusion_matrix_values(confusion_matrix)
  return(conf_matrix[1] / (conf_matrix[1] + conf_matrix[4]))
}
f1 <- function(confusion_matrix){
  conf_matrix <- confusion_matrix_values(confusion_matrix)
  rec <- recall(confusion_matrix)
  prec <- precision(confusion_matrix)
  return(2 * (rec * prec) / (rec + prec))
}
```

@@

```{r get_result_function, warning = FALSE, message = FALSE, cache = TRUE}
library(rpart)
get_result <- function(dataset_list, imputation_fun){

@@

```{r warning=FALSE, cache = TRUE}
  library(knitr)
  results <- c(list(0),list(0),list(0),list(0),list(0))
  results[[1]] <- readRDS('./part_results/res1_new.rds')
  results[[2]] <- readRDS('./part_results/res2_new.rds')
  results[[3]] <- readRDS('./part_results/res3_new.rds')
  results[[4]] <- readRDS('./part_results/res4_new.rds')
  results[[5]] <- readRDS('./part_results/res5_new.rds')

  result_table <- function(ds_it){
    d <- data.frame(matrix(ncol = 7, nrow = 0))
    colnames(d) <- c("imputation", "accuracy", "precision", "recall", "f1", "imp_time", "mod_time")
    for (i in 1:length(imputations)){
      if (length(results[[i]][[ds_it]]) != 1){ # length equal 1 means "ERROR" was generated in partial results 
        d[i,] <- c(results[[i]][[ds_it]]$imp_method,
               round(as.numeric(results[[i]][[ds_it]]$classification_report$accuracy),3),   
               round(as.numeric(results[[i]][[ds_it]]$classification_report$precision),3),
               round(as.numeric(results[[i]][[ds_it]]$classification_report$recall),3),
               round(as.numeric(results[[i]][[ds_it]]$classification_report$f1),3),
               round(as.numeric(results[[i]][[ds_it]]$imputation_time),3),
               # @TODO konwersja jednostek, as.numeric nie rozroznia jednostek czasu
               round(as.numeric(results[[i]][[ds_it]]$modelling_time),3)) 
      }
      else{ # for error input imputation name
        if (i==3){
          d[i,1] <- "imputation_fun_mice" 
        }
        if (i==4){
          d[i,1] <- "imputation_fun_missForest" 
        }
        if (i==5){
          d[i,1] <- "imputation_fun_vim" 
        }
      }
    }
  }

  results[[1]]
  # change i bound to number of datasets 
  for (i in 1:length(results[[1]])){
    kable(result_table(i), caption = paste("Dataset id: ", results[[2]][[i]]$dataset_id, sep = ""))
  }

@@

```{r imputation_times_counting, cache = TRUE}
ndatasets <- length(results[[1]])
nimputations <- length(imputations)
imputation_names <- c("remove", "median", "mice", "missForest", "VIM")
dataset_ids <- rep(NULL, ndatasets)
for(i in 1:ndatasets){
  dataset_ids[i] <- results[[2]][[i]]$dataset_id
}

imputation_times <- data.frame(rep(0, 14))
for (imputation_id in 1:nimputations){
  imp_id_times <- rep(NULL, ndatasets)

  for(dataset_id in 1:ndatasets){
    if("imputation_time" %in% names(results[[imputation_id]][[dataset_id]])){
      imp_time <- results[[imputation_id]][[dataset_id]]$imputation_time
      imp_time <- as.numeric(imp_time, units="secs")
      imp_id_times[dataset_id] <- imp_time
    }
  }
  imputation_times <- cbind(imputation_times, imp_id_times)
}

imputation_times[1] <- dataset_ids
colnames(imputation_times) <- c("dataset_id", imputation_names)
imputation_times$dataset_id <- as.factor(imputation_times$dataset_id)
knitr::kable(imputation_times)
```

```{r imputation_times_plot}
library(ggplot2)

colors <- c("remove" = "orange", "median" = "cyan", "mice" = "green",
            "missForest" = "red", "VIM" = "blue")

require(scales)
ggplot(data = imputation_times, aes(x = dataset_id)) +
  geom_point(aes(y = remove), color = colors[1], size = 2, shape = 18) +
  geom_point(aes(y = median), color = colors[2], size = 2, shape = 16) +
  geom_point(aes(y = mice), color = colors[3], size = 2, shape = 15) +
  geom_point(aes(y = missForest), color = colors[4], size = 2, shape = 17) +
  geom_point(aes(y = VIM), color = colors[5], size = 2, shape = 19) +
  ggtitle("Datasets' imputations times") +
  theme_gray() +
  scale_y_continuous(trans = log2_trans(),
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +
  labs(x = "Dataset Id",
       y = "Imputation time [in seconds]",
       color = "Legend") +
  scale_color_manual(name = ":-)", values = colors) +
  theme(legend.position="right",
        plot.title = element_text(hjust = 0.5))
```
